---
title: "R Notebook"
output: html_notebook
---

# Mixed-Effects Models in R 

```{r, echo=FALSE, results='hide', message=FALSE}
library(tidyverse)
```

We will be working with California Housing Prices (see more details on [Kaggle](https://www.kaggle.com/datasets/camnugent/california-housing-prices)). The data set is a modified version from the following paper: 

Pace, R. Kelley, and Ronald Barry. "Sparse spatial autoregressions." Statistics & Probability Letters 33.3 (1997): 291-297.

## Variables 

1. longitude: A measure of how far west a house is; a higher value is farther west
2. latitude: A measure of how far north a house is; a higher value is farther north
3. housingMedianAge: Median age of a house within a block; a lower number is a newer building
4. totalRooms: Total number of rooms within a block
5. totalBedrooms: Total number of bedrooms within a block
6. population: Total number of people residing within a block
7. households: Total number of households, a group of people residing within a home unit, for a block
8. medianIncome: Median income for households within a block of houses (measured in tens of thousands of US Dollars)
9. medianHouseValue: Median house value for households within a block (measured in US Dollars)
10. oceanProximity: Location of the house w.r.t ocean/sea

```{r}
df = read_csv('https://raw.githubusercontent.com/ageron/handson-ml/master/datasets/housing/housing.csv')

head(df)

```

